Getting the Ball Rolling: Producing a Foundation Text for a Universal Corpus of the World's Languages

### 2014-02-28 docs/acl-2014/paper.tex
Continued work on paper.

\documentclass[11pt]{article}
\usepackage{eacl2014}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{color}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}

\usepackage{listings}
\usepackage{fancyvrb}

\usepackage{color}
\definecolor{gray}{rgb}{0.4,0.4,0.4}
\definecolor{darkblue}{rgb}{0.0,0.0,0.6}
\definecolor{cyan}{rgb}{0.0,0.6,0.6}
\definecolor{orange}{rgb}{1,0.5,0}

@@

\special{papersize=210mm,297mm} % to avoid having to use "-t a4" with dvips 
%\setlength\titlebox{6.5cm}  % You can expand the title box if you really have to

\title{uniWaC: Compiling the Foundation Text for the WaCky Universal Corpus}

\author{Susanne Fertmann\textsuperscript{$\alpha$}, Guy Emerson\textsuperscript{$\beta$}, Liling Tan\textsuperscript{$\alpha$}, Alexis Palmer\textsuperscript{$\alpha$} and Michaela Regneri\textsuperscript{$\alpha$} \\
  Universit{\"a}t des Saarlandes\textsuperscript{$\alpha$} / Campus, 66123 Saarbrücken, Germany \\
  Deutsches Forschungszentrum f{\"u}r Künstliche Intelligenz (DFKI)\textsuperscript{$\beta$} / \\ Stuhlsatzenhausweg 3, 66123 Saarbrücken, Germany \\
  {\tt s9sufert@stud.uni-saarland.de, emerson@coli.uni-saarland.de,} \\
  {\tt liling.tan@uni-saarland.de}}

@@

\begin{document}
\maketitle
\begin{abstract}
A grand aim of linguistics is to seek a universal theory of human language and the opposing relativist view of linguistics seek to prove otherwise. To accomplish either goal, the compilation of a Universal Corpus with significant data from a large variety of languages is necessary. The Web contains vast amounts of linguistic data however it is largely saturated by English content (\textgreater50\%). Nonetheless, there are websites that contains small amount of data in a large number of languages. To build the foundation text for a Universal Corpus, we crawled and cleaned texts from several web sources that contains linguistic data from multiple languages and merge them with existing corpora collections.This paper describes the progress of compiling, cleaning and standardizing the foundation texts for the Universal Corpus (\texttt{uniWaC}) and briefly describes the ongoing work to merge our compilation with existing corpora collections.
\end{abstract}

\section{Introduction}
Abney and Bird (2010) posed a grand challenge to build a Universal Corpus that will include as many of the world's languages as possible, in a consistent structure that permits crosslingual processing and analysis. Ideally, the Universal Corpus would be a complete digitization of every human language. To empirically prove or disprove the existence of a universal theory of human languages, a Universal Corpus is necessary.

@@

\subsection{Wikipedia Dumps}

@@

\section{Access and Copyrights}

\section{Representation and Universality}
This is we report the counts and size of corpus.

\section{Ongoing Work}

Currently, the uniWaC project is continually adding more data from the LCC Leipzig Corpora. Finally, the first phase of the uniWaC will end with the implementation of unsupervised tokenizer (e.g. Chung and Gildea, 2009) such that initial experiments on crosslingual analysis can be carried out to advance the grand aim of a unified linguistic theory.

% TODO: use proper bibtex !!!!
\section*{References}
Steven Abney and Steven Bird. 2010. The Human Language Project: Building a Universal Corpus of the World’s Languages. In Proceedings of the 48th Annual Meeting of the Association for Computational Linguistics. Uppsala, Sweden.
\\\\
Steven Abney and Steven Bird. 2011. Towards a data model for the Universal Corpus. In Proceedings of the 4th Workshop on Building and Using Comparable Corpora: Comparable Corpora and the Web. Portland, Oregon.
\\\\
Michele Banko and Eric Brill. 2001. Michele Banko and Eric Brill. 2001. Scaling to very very large corpora for natural language disambiguation. In Proceedings of the 39th Annual Meeting on Association for Computational Linguistics (ACL '01). Association for Computational Linguistics, Stroudsburg, PA, USA, 26-33.
\\\\
Marco Baroni, Silvia Bernardini, Adriano Ferraresi and Eros Zanchetta. (2008). The WaCky wide web: A collection of very large linguistically processed web-crawled corpora. Language Resources and Evaluation, 43(3), 209–231.
\\\\
Tagyoung Chung and Daniel Gildea. 2009. Unsupervised tokenization for machine translation. In Proceedings of the 2009 Conference on Empirical Methods in Natural Language Processing: Volume 2 - Volume 2 (EMNLP '09), Vol. 2. Association for Computational Linguistics, Stroudsburg, PA, USA, 718-726.
\\\\
Adriano Ferraresi. 2007. Building a very large corpus of English obtained by Web crawling: ukWaC. Master Thesis, University of Bologna
\\\\
Jörg Tiedemann. 2012. Parallel Data, Tools and Interfaces in OPUS. In Proceedings of the 8th International Conference on Language Resources and Evaluation. Istanbul, Turkey.
\\\\
Liling Tan and Francis Bond. 2011. Building and Annotating the Linguistically Diverse NTU-MC (NTU-Multilingual Corpus). In Proceedings of The 25th Pacific Asia Conference on Language, Information, and Computation. Singapore, Singapore.

>>>>

\documentclass[11pt]{article}
\usepackage{acl2014}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}

\bibliographystyle{acl}

\usepackage{enumitem}
\usepackage{listings}
\usepackage{fancyvrb}
\usepackage{color}
\definecolor{gray}{rgb}{0.4,0.4,0.4}
\definecolor{darkblue}{rgb}{0.0,0.0,0.6}
\definecolor{cyan}{rgb}{0.0,0.6,0.6}
\definecolor{orange}{rgb}{1,0.5,0}

@@

\setlength\titlebox{5cm}

\title{Getting the Ball Rolling: Producing a Foundation Text for a Universal Corpus of the World's Languages}

\author{Liling Tan, Guy Emerson, Susanne Fertmann, Alexis Palmer and Michaela Regneri \\
  Universit{\"a}t des Saarlandes \\
  Campus, 66123 Saarbr{\"u}cken, Germany \\
  {\tt s9sufert@stud.uni-saarland.de, emerson@coli.uni-saarland.de,} \\
  {\tt liling.tan@uni-saarland.de}}

@@

\begin{document}
\maketitle
\begin{abstract}
The study of endangered languages is limited by a lack of data. Existing corpora collections are limited in the range of languages covered, in standardisation, or in machine-readability. This makes the situation even worse for the computational linguist, especially one who would like to take a cross-linguistic or typological approach. We first survey existing efforts to compile cross-linguistic resources, then describe our own approach and give an example application - language clustering. To build the foundation text for a Universal Corpus, we crawled and cleaned texts from several web sources that contain data from a large number languages, and converted them into a standardised form consistent with the guidelines set out by Abney and Bird (2010). The resulting corpus is more easily-accessible and machine-readable than any of the underlying data sources, and represents a significant base corpus for researchers to draw on and add to in the future.
\end{abstract}

\section{Introduction}

\newcite{abneybird2010} posed the grand challenge of building a Universal Corpus, including all of the world's languages, in a consistent structure.

\section{Related Work}

@@

\subsection{Wikipedia}

@@

\subsection{Leipzig Corpora Collection}

Do we want to mention this?

\section{Copyright Issues}

Creative Commons Licence, etc.

\section{Representation and Universality}

Number of languages, size of corpus, etc.

\section{Language Clustering}

This would be an example application, if we have time...

\section{Future Work}

Other corpora we could work on...

\section{Conclusion}

Summarise what we've done!

\bibliography{references}
